\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-10-13 paper.tex
Some refs

\section*{ARGs and local trees}
% TODO mention Yamato here? I'm sure there were some interesting points
% about local trees in that paper
Local trees, describing the genetic genealogy of a sample
at a particular location along the genome, are
embedded within an ARG, and the relationship
between the two is subtle and important.
% An ARG is sometimes referred to as being equivalent to a set of
% local trees along the genome [TODO citation], but the connection
% between the two is subtle.
% In order for the mapping to be one-to-one, so that the original
% gARG can be exactly recovered from a set of local trees and
% their genome coordinates,
% some specific properties of the ARG and the trees are required.
Note that many authors use the term ``marginal''
trees~\citep[e.g.][AND OTHERS]{griffiths1996ancestral,minichiello2006mapping}
which we avoid due to the potential confusion with the
statistical concept of marginal distributions
(which could lead to interpretation as an integrated tree over many positions).

>>>>

\section*{ARGs and local trees}
Local trees, describing the genetic genealogy of a sample
at a particular location along the genome, are
embedded within an ARG, and the relationship
between the two is subtle and important.
Note that many authors use the term ``marginal''
% could list loads here, but not much point.
trees~\citep[e.g.][]{griffiths1996ancestral,minichiello2006mapping,kelleher2016efficient}
which we avoid due to the potential confusion with the
statistical concept of marginal distributions
(potentially leading to interpretation as an integrated tree over many positions).
